### 2016-12-02 methodsPaper/tex/materialsAndMethods.tex
Edits to Materials & Methods
added ICD-10 codes
need to verify Depression

As with the original ITHIM implementation we employed a comparative
risk analysis (CRA) across scenarios defined by mean active
transportation time, i.e., walking and cycling.  To do so we
investigate the proportional change in national disease burden between
the baseline model and a given alternative scenario, i.e., the
population attributable fraction, $\af$.  The population attributable
fraction is defined below and computed for each disease included in
the model, namely Breast Cancer, Colon Cancer, Depression, Dementia,
Diabetes and Cardiovascular disease.  For readability we omit an index
indicating disease.

@@

Within each age-sex class the non-travel-related exposure is modeled
with a \logNormal{} distribution.  The age-sex specific mean ratios,
$r_{ij} = \frac{\mu_{ij}}{\mu_0}$ and $\gamma$ are estimated from the
American Time USe Survey data \cite{ATUS}.

@@

To test the new implementation of ITHIM's active transportation
component, we used the UW national metro population estimates for
active travel time (walking and cycling) as the baseline. We obtained
active travel time input parameters for alternate scenarios using
states with large sample sizes. From these examples we were able to
approximate low and high active travel scenarios. Finally we applied
these active travel times to the US metro population to perform the
comparative risk assessment against the baseline US numbers. We then
examined the sensitivity of disease burden estimates to input
parameters including the active travel time and non-travel activity.

>>>>

As with the original ITHIM implementation we, employed a comparative
risk assessment (CRA) across scenarios defined by mean active
transportation time, i.e., combined walking and cycling.  To do so we
investigate the proportional change in national disease burden between
the baseline model and a given alternative scenario, i.e., the
population attributable fraction, $\af$.  The population attributable
fraction is defined below and computed for each disease (ICD-10) included in
the model, namely Breast Cancer (C50), Colon Cancer (C18-C21), Depression (??), Dementia (G30),
Diabetes (E10-E14) and Cardiovascular disease (I10, I12, I15, I20-I25, I30-I31, I33, I40).  For readability we omit an index
indicating disease.

@@

Within each age-sex class the non-travel-related exposure is modeled
with a \logNormal{} distribution.  The age-sex specific mean ratios,
$r_{ij} = \frac{\mu_{ij}}{\mu_0}$ and $\gamma$ are estimated from the
American Time Use Survey data \cite{ATUS}.

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Tue Nov  8 09:38:46 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & M & F \\
  \hline
0-4 & 0.00 & 0.00 \\
  5-14 & 0.00 & 0.00 \\
  15-29 & 0.97 & 1.00 \\
  30-44 & 1.04 & 1.12 \\
  45-59 & 0.95 & 0.99 \\
  60-69 & 0.90 & 0.94 \\
  70-79 & 0.83 & 0.88 \\
  80+ & 0.72 & 0.77 \\
   \hline
\end{tabular}
\end{table}

@@

To test the new implementation of ITHIM's active transportation
component, we used the US national metro population estimates for
active travel time (walking and cycling) as the baseline. We obtained
active travel time input parameters for alternate scenarios using
states with large sample sizes. From these examples we were able to
approximate low and high active travel scenarios. Finally, we applied
these active travel times to the US metro population to perform the
comparative risk assessment against the baseline US numbers. We then
examined the sensitivity of disease burden estimates to input
parameters including the active travel time and non-travel activity.
